\documentclass[a4paper,10pt, bibliography=totocnumbered]{scrreprt}

\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}

\usepackage{graphicx}
\usepackage{pdfpages}
%\usepackage{subfig}
%\usepackage{microtype}
\usepackage{tabularx}
%\usepackage{amsmath, textcomp}

% Custom packages
\usepackage[numbers]{natbib}
\usepackage{longtable}
\usepackage{ragged2e}
%\usepackage{tikz}
%\usetikzlibrary{positioning}
%\usepackage{pdflscape}
%\usepackage{rotating}

\usepackage{glossaries} 

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,        % color of internal links
%    citecolor=green,        % color of links to bibliography
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}


%% Title Page
\makeatletter
\renewcommand{\maketitle}{\begin{titlepage}
    \vskip 10\p@
    \hbox{
      \vrule depth 0.99\textheight
        \mbox{\hspace{2em}}
      \vtop{
        \vskip 10\p@
        \hspace{4pt}
        \vskip 50\p@
        \begin{flushleft}
          \Large \@author \par
        \end{flushleft}
        \vskip 50\p@
        \begin{flushleft}
          \huge \bfseries \@title \par
        \end{flushleft}
        \begin{flushleft}
          \Large \bfseries \@subtitle \par
        \end{flushleft}
        \vskip 70\p@
        \begin{flushleft}
          \Large \@publishers \par
        \end{flushleft}
        \vskip 50\p@
        \begin{flushleft}
          \Large \@date \par
        \end{flushleft}
        }}
  \end{titlepage}
}
\makeatother

\author{Author 1, Author n}
\title{Title }
\subtitle{Technical Report}
\publishers{\textbf{Advisor University of Heidelberg}\\ Prof. Dr. Barbara Paech, Michael Anders}
\date{mm dd, year}



% Deutsche Absaetze:
\parindent 0pt
\parskip 12pt

\textwidth145mm
\setlength{\oddsidemargin}{0.7cm}
\setlength{\topmargin}{-0.5cm}
\setlength{\textheight}{22.5cm}

\begin{document}
\maketitle

\include{./content/0-Abstract}

\tableofcontents

\input{./content/1-Introduction}
\input{./content/2-Chapter2}
\input{./content/3-Chapter3}
\input{./content/Thema7Buerkel}
\input{./content/10-Conclusion}

%% Bibliography
\bibliographystyle{plainnat}
%\bibliography{literature.bib}%Bibliography file name

\begin{thebibliography}{9}

\bibitem{KunChen2005} Chen, K, Zhang, W., Zhao, H.: An approach to constructing feature models based on requirements clustering.
In: 13th IEEE International Conference on Requirements Engineering (RE05). pp. 31-40. (2005)

\bibitem{RichtigesZitierenTUDresden} Institut für Geographie   
Lehrstuhl für Allgemeine Wirtschafts- und Sozialgeographie: An Hinweise zum wissenschaftlichen Arbeiten.
\url{http://www.geogr.uni-jena.de/fileadmin/Geoinformatik/Lehre/backup_05_2007/pdf-dokumente/Skript_WissArbeiten.pdf}

% Sources Topic 2 Start
\bibitem{Ciurumelea.2017} A. Ciurumelea, A. Schaufelbühl, S. Panichella and H. C. Gall, "Analyzing reviews and code of mobile apps for better release planning" 2017 IEEE 24th International Conference on Software Analysis, Evolution and Reengineering (SANER), 2017, pp. 91-102, doi: 10.1109/SANER.2017.7884612.
  
\bibitem{Scalabrino.2019} S. Scalabrino, G. Bavota, B. Russo, M. D. Penta and R. Oliveto, "Listening to the Crowd for the Release Planning of Mobile Apps," in IEEE Transactions on Software Engineering, vol. 45, no. 1, pp. 68-86, 1 Jan. 2019, doi: 10.1109/TSE.2017.2759112.

\bibitem{Villarroel.2016}L. Villarroel, G. Bavota, B. Russo, R. Oliveto and M. Di Penta, "Release Planning of Mobile Apps Based on User Reviews," 2016 IEEE/ACM 38th International Conference on Software Engineering (ICSE), 2016, pp. 14-24, doi: 10.1145/2884781.2884818.
  
\bibitem{Mahmud.2019}O. Mahmud, N. T. Niloy, M. A. Rahman and M. S. Siddik, "Predicting an Effective Android Application Release Based on User Reviews and Ratings," 2019 7th International Conference on Smart Computing \& Communications (ICSCC), 2019, pp. 1-5, doi: 10.1109/ICSCC.2019.8843677.

\bibitem{Noei.2019}E. Noei, F. Zhang and Y. Zou, "Too Many User-Reviews! What Should App Developers Look at First?," in IEEE Transactions on Software Engineering, vol. 47, no. 2, pp. 367-378, 1 Feb. 2021, doi: 10.1109/TSE.2019.2893171.

\bibitem{Aslam.2020}N. Aslam, W. Y. Ramay, K. Xia and N. Sarwar, "Convolutional Neural Network Based Classification of App Reviews," in IEEE Access, vol. 8, pp. 185619-185628, 2020, doi: 10.1109/ACCESS.2020.3029634.

\bibitem{Suprayogi.2018}E. Suprayogi, I. Budi and R. Mahendra, "Information Extraction for Mobile Application User Review," 2018 International Conference on Advanced Computer Science and Information Systems (ICACSIS), 2018, pp. 343-348, doi: 10.1109/ICACSIS.2018.8618164.
% Sources Topic 2 End

% Sources Topic 4 Start
\bibitem{Bakiu2017} Bakiu, E., Guzman, E.: Which Feature is Unusable? Detecting Usability and User Experience Issues from User Reviews.
In: 25th International Requirements Engineering Conference Workshops (REW). pp. 182-187. (2017)

\bibitem{Hedegaard2013} Hedegaard, S., Simonsen, J. G.: Extracting usability and user experience information from online user reviews.
In: Proceedings of the SIGCHI Conference on Human Factors in Computing Systems, pp. 2089-2098. (2013).

\bibitem{Weichbroth2019} Weichbroth, P. Baj-Rogowska, A.: Do Online Reviews Reveal Mobile Application Usability and User Experience? The Case of WhatsApp. In: 2019 Federated Conference on Computer Science and Information Systems (FedCSIS), pp. 747-754. (2019).

\bibitem{Zhao2021} Zhao, H et al: A machine learning-based sentiment analysis of online product reviews with a novel term weighting and feature selection approach.
In: Information Processing \& Management, Volume 5, Issue 5. (2021).

\bibitem{Bafna2013} Bafna, K., Toshniwal, D.: Feature based Summarization of Customers' Reviews of Online Products.
In: Procedia Computer Science, Volume 22, pp. 142-151. (2013).

\bibitem{Qian2016} Qian, Z., Wan, C., Chen, Y.: Evaluating quality-in-use of FLOSS through analyzing user reviews.
In: 17th International Conference on Software Engineering, Artificial Intelligence, Networking and Parallel/Distributed Computing (SNPD). pp. 547-552. (2016)

\bibitem{Guzman2014} Guzman, E., Maalej, W.: How Do Users Like This Feature? A Fine Grained Sentiment Analysis of App Reviews.
In: 22nd International Requirements Engineering Conference (RE). pp. 153-162. (2014)

\bibitem{Socher2013} Socher, R., Perelygin, A., Wu, J. Y., Chuang, J., Manning, C. D., Ng, A. Y.: Recursive deep models for semantic compositionality over a sentiment treebank.
In: Proceedings of the conference on empirical methods in natural language processing (EMNLP). vol. 1631, pp. 1642. (2013)

\bibitem{Bevan2008} Bevan, N.: Classifying and selecting UX and usability measures.
In: International Workshop on Meaningful Measures: Valid Useful User Experience Measurement. pp. 13-18. (2008)

\bibitem{Ketola2008} Ketola, P. in Proceedings of the Open Workshop on Valid Useful User Experience Measurement: ser. VUUM (2008)

\bibitem{BargasAvila2011} Bargas-Avila, J. A., Hornbæk, K.: Old wine in new bottles or novel challenges: A critical analysis of empirical studies of user experience.
In: Proceedings of the SIGCHI Conference on Human Factors in Computing Systems. pp. 2689-2698. (2011)

\bibitem{Shneiderman1996} Shneiderman, B.: The eyes have it: a task by data type taxonomy for information visualizations.
In: Proceedings 1996 IEEE Symposium on Visual Languages. pp. 336-343. (1996)
% Sources Topic 4 End

% Sources Topic 7 Start
\bibitem{Antoniol2008} Antoniol, G., Ayari, K., Di Penta, M., Khomh, F., Guéhéneuc, Y.: Is it a Bug or an Enhancement? A Text-based Approach to Classify Change Requests.
In: CASCON '08: Proceedings of the 2008 conference of the center for advanced studies on collaborative research: meeting of minds. pp. 304-318 (2008)

\bibitem{Kallis2021} Kallis, R., Di Sorbo, A., Canfora, G., Panichella, S.: Predicting Issue Types on GitHub.
In: Science of Computer Programming, vol. 205, pp. 102598 (2021)

\bibitem{IEEE} IEEE Xplore, https://ieeexplore.ieee.org/, accessed: see table

\bibitem{ACM} Association for Computing Machinery - Digital Library, https://dl.acm.org/ accessed: see table

\bibitem{Otoom2019} Otoom, A. F., Al-jdaeh, S., Hammad, M.: Automated classification of software bug reports.
In: ICICM 2019: Proceedings of the 9th International Conference on Information Communication and Management, pp. 17-21 (2019)

\bibitem{Ahmed2021} Ahmed, H. A., Bawany, N. Z., Shamsi, J. A.: CaPBug-A Framework for Automatic Bug Categorization and Prioritization Using NLP and Machine Learning Algorithms.
In: IEEE Access, vol. 9, pp. 50496-50512 (2021)
%Sources Topic 7 End
\end{thebibliography}

\listoffigures

\listoftables

\end{document}          
